Refinements for open automata

### 2022-04-20 2021-Refinement/paper/refinementarticle.tex
composition is a refinement thm (+lemma tracked holes)

\TODO{example}

@@

@@

- composition is a refinement (under which condition? non-blocking composition?)

@@

>>>>

\begin{lemma}[Tracked holes] By construction, if an automaton is the refinement of another one, it is also a refinement by tracking less holes.
\[\wrel{A_1}{A_2}{H} \land H'\subseteq H \implies \wrel{A_1}{A_2}{H'}\]
\end{lemma}
\TODO{example}

@@

Open automata compositionis a refinement where
the tracked holes are the holes of the base automaton minus the composed hole.
\begin{theorem}[Composition is a refinement]\label{thm:Composition}
Let $A_1$ and  $A_2$  be three two automata with $J_1$ the set of holes of $A_1$.
Suppose that \(k \in J_1\) and that \(A_1\subst{A_2}{k}\) is non-blocking. We have:
\[ \wrel{A_1\subst{A_2}{k}}{A_1}{J_1\setminus \{k\}}\]
\end{theorem}

@@

@@

\section{Proof that Composition is a refinement (Theorem~\ref{thm:Composition})}
